Spatiotemporal Optimization of Cosmological Particel-Mesh Simulation

### 2023-02-01 docs/papers/sto/sto.tex
Draft: just a few sentences

@@

>>>>

We perform parallel training using a number of nodes that each hosts multiple
GPU devices.
The training on a given snapshot is performed on a single GPU device.
The gradients are collected and averaged to update the STO parameters.
To make sure that each individual training in a parallel run finishes in similar
time, they share the same number of time steps.

@@

\subsection{SO function}

We use the \texttt{PySR} \citep{PySR, Cranmer2020} symbolic regression code to
fit for an analytic function expression of the SO neural network.
